The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2024-02-29 analysis/paper/paper.qmd
Disable keywords and highlights
Update setup code chunk

<!-- The following code display values from the YAML header above. -->

Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`

@@

```{r setup}
#| include: false

# TODO remove unused packages after all analysis has been translated into functions
# Load packages ----
## List packages to be loaded
packages <- c(
  "here",
  "tidyverse", "widyr", "readxl",   # Data manipulation and visualisation
  "furrr",                          # Parallel use of purrr::map() functions
  "tidytext", "SnowballC", "tm",    # Text processing and analysis
  "topicmodels", "LDAvis", "tsne",  # Topic modeling
  "tidygeocoder",                   # Working with spatial data
  "igraph", "ggraph", "DiagrammeR"  # Network analysis and visualization
)

## Load required packages, install them if needed
for (package in packages) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package,  "http://cran.us.r-project.org")
  }
  library(package, character.only = TRUE)
}

# TODO should this be replaced with a call to `library(mintEMU)`?
# Load analysis functions ----
devtools::load_all(".")
```

```{r load-data}
#| include: false

# TODO merge into setup code chunk

# Load data for analysis
data(emu_metadata)  # Thesis metadata
data(emu_raw)       # Raw text data
data(emu_clean)     # Cleaned text data

# Join metadata and cleaned text data
emu <- emu_metadata |> 
  left_join(emu_raw, by = "ID") |> 
  left_join(emu_clean, by = "ID")

theses_all_per_year <- read_csv(file = here("analysis", "data", "derived_data", "emu-theses-per-year.csv"))

word_counts <- get_word_counts(emu, text_col = "text_clean")

>>>>

<!-- The following code can be used to show values from the YAML header in DOCX output. -->

<!-- Keywords: `r rmarkdown::metadata$keywords` -->

<!-- Highlights: `r rmarkdown::metadata$highlights` -->

@@

```{r}
#| label: setup
#| include: false

# Load packages ----
library(tidyverse)

# Load analysis functions ----
## TODO should this be replaced with a call to `library(mintEMU)`?
devtools::load_all(".")

# Load data ----
data(emu_metadata)  # Thesis metadata
data(emu_raw)       # Raw full text data
data(emu_clean)     # Cleaned full text data

# Join metadata and cleaned text data ----
emu <- emu_metadata |> 
  left_join(emu_raw, by = "ID") |> 
  left_join(emu_clean, by = "ID") |> 
  select(-c(grad_sem, title, subtitle, abstract)) |> 
  rename(title = full_title) |> 
  select("ID", "title", everything())

# Get counts per corpus ----
theses_all_per_year <- read_csv(file = here::here("analysis", "data", "derived_data", "emu-theses-per-year.csv"))
word_counts <- get_word_counts(emu, text_col = "text_clean")
```
